Pillar 2 - Topic Modeling

### 2019-05-03 Pillar 2 - Topic Modeling.Rmd
cleaning pillar 2

##Functions for internal faceting
```{r function reorder_within & co., echo = FALSE, eval = TRUE}

@@

##Loading data
We load the environment `output/data_pillar_2.RDATA`. It contains the data sets:
`d_course`, `d_transcript`, and a list `d_text` with the textual data for catalogues and manuals (for $catalogues, $manuals we have (`Course ID`, `year`, `word_original`, `word`) ).

For `d_text` we keep only the most recent year.
```{r import data, eval = TRUE}
#load
#load("output/data_pillar_2.RDATA")
load("./Output/d_text.RDATA")
```

@@

# LDA
##Setup
###Cast DTM
The function `my_cast_dtm` casts our dataframes into a DTM.
```{r my_cast_dtm, eval = TRUE}
my_cast_dtm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

d_cast <- d_text %>% map(my_cast_dtm)

rm(my_cast_dtm)
```
###Controls
The control parameters we use are:
```{r controls, eval = TRUE}
my_control <- list(

  nstart = 10,
  seed   = 1 : 10,
  best   = TRUE,

  burnin = 100,
  iter   = 2000,
  thin   = 100

)
```
The control parameters we use for fast testing are:
```{r fast control}
my_control_fast <- list(

@@

##Ideal Number of Topics Package Test
To decide the number of topics to discover, we run three different tests.
###Function
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

  FindTopicsNumber(

  dtm = data_cast,
  topics = n_topics,
  metrics = c("CaoJuan2009", "Arun2010", "Deveaud2014"),
  method = "Gibbs",
  control = my_control,
  mc.cores = 4L

  )

}
```
###Train
```{r package test on topics, cache = TRUE}
#Start timer
start.time <- Sys.time()

#
##apply my_FindTopicsNumber
result_topic_test <- as_tibble(map(.x = d_cast, .f = my_FindTopicsNumber, n_topics = seq(from = 5, to = 100, by = 2)))

#Stop timer
end.time <- Sys.time()
print(end.time - start.time)

#
##Save results
#save(result_topic_test,
#     file = "Output/LDA_ntopics.RDATA") #this file still contains old results.
```
Previous separate experiments (from 20, to 40, by 5 topics) had the following time:
* Overview:     22min 
* Description:  11min 
* Manuals:      5.5hrs

###Graph 
We examine the result of the experiment by plotting them on a graph.
```{r LDA number topics plot}
#load("Output/LDA_ntopics.RDATA")

result_topic_test %>% map(.f = ldatuning::FindTopicsNumber_plot) #order is: Overview, Manuals, Description
```
From the results we see that the ideal number of topics is somewhere between 35 and 40.

@@

###Functions for models (extract_dtm, get_distributions, perplexity)
The following functions are used as input in a map to compute and evaluate topic models. 
```{r getting gamma and beta, eval = TRUE}
#extract dtm
extract_dtm <- function(origin) d_cast[[origin]]

@@

The following functions allow us to inspect the results from our models(inspect distributions and get kw):
```{r inspection functions, eval = TRUE}
 # get_top_match <- function(d_distribution){
 # 
 #  #save user input as string
 #  name_selected <- deparse(substitute(d_distribution)) #takes Gamma or Beta
 #  beta_gamma_sym <- tolower(name_selected)             #transforms to "gamma" or "beta"
 # 
 #  #Compute Case (Beta or Gamma, respectively)
 #  grouping         <- ifelse( name_selected == "Beta",  "topic", "document")
 #  objects_to_group <- ifelse( name_selected == "Beta",  "term",  "topic"   )
 #  top_num          <- ifelse( name_selected == "Beta",   10,      5       ) #select how many terms or topics(respectively) to show
 # 
 #  #
 #  ## DATA
 #  data.frame(d_distribution) %>%
 #    group_by(!!sym(grouping)) %>%
 #    top_n(top_num, !!sym(beta_gamma_sym)) %>%
 #    select(!!sym(grouping), !!sym(objects_to_group)) %>%
 #    group_by(!!sym(grouping)) %>%
 #    summarise(top = list(!!sym(objects_to_group)))
 # }

@@

```
###Training Models
We train the LDA for different numbers of topics (5 to 250 by 5), we save the resulting 50 models under `topic_model`, along with the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words.
```{r LDA fit, cache = TRUE, eval = TRUE}
topic_numbers <- seq(from = 5, to = 15, by = 5)

test_topic_model <- tibble( #CHANGE NAME TO: topic_model

  #repeat each topic number twice (once for catalogues and once for manual)
  n_topic = rep(topic_numbers, each = 2) # from = 5, to = 250, by = 5

  ) %>%
  mutate(Origin     = rep(c("catalogues", "manuals"), 3),         # should be 50
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

@@

         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast), #my_control

@@

# Clean workspace

# rm(extract_dtm, get_distributions, my_perplexity,
#    get_top_terms_topic, get_top_topics_course, get_kw)

@@

##Plots - Model Evaluation
To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin){

  #data
  test_topic_model %>%

##Saving model_data:
We save our tibble with all the information.
```{r save, eval = T}
save(test_topic_model, file = "Output/test_topic_model.RDATA" )
# save(topic_model, file = "Output/topic_model.RDATA" ) #needs to be renamed to match what is currently test_topic_model
```

>>>>

##Loading data
We load a list `d_text` with two tibbles of textual data for catalogues and manuals. That is, for $catalogues and $manuals we have a tibble with the following columns: `Course ID`, `year`, `word_original`, `word`.

We also load the environment `Output/data_pillar_2.RDATA` containing the data sets`d_course` and `d_transcript` that we will need to prepare some imputs for our App.
```{r import data, eval = TRUE}
#load
load("./Output/d_text.RDATA")
load("./Output/data_pillar_2.RDATA") #used for app
```
##Helpers
###Preparation of course_title vector
```{r course titles, eval = TRUE}
#Clean titles
course_titles <-  d_text$catalogues %>%
  select(`Course ID`, `Course Title`, department) %>% 
  distinct

empty_titles <- course_titles %>% filter(`Course Title` == "")
```
####Uniform titles
We do not have the course codes for all courses, in that case we use the course titles as identifiers, for more pleasant display to the user, we will make course labels uniform, for unknown codes we give the label "unknown" and attatch the title as title. 
```{r attatch titles}
uniform_course_labels <- course_titles %>% mutate(`c_title`= case_when(is.na(`Course Title`) ~ `Course ID`,
                                              T ~ `Course Title`),
                         `Course ID` = case_when(str_length(`Course ID`) == 7 ~ `Course ID`,
                                                 T ~ "unknown"),
                         `Course Title` = c_title
                         ) %>% select(-c_title)
```
###Functions for internal faceting
```{r function reorder_within & co., echo = FALSE, eval = TRUE}

@@

@@

# LDA
##Setup
###Cast DTM
The function `my_cast_dtm` casts our dataframes (catalogues and manuals) into a DTM.
```{r my_cast_dtm, eval = TRUE}
#Function
my_cast_dtm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

#Application
d_cast <- d_text %>% map(my_cast_dtm)

#Clean workspace
rm(my_cast_dtm)
```
###Controls
The control parameters we will use to train our LDA model are:
```{r controls, eval = TRUE}
my_control <- list(

  nstart = 20,
  seed   = 1 : 20, #must have length nstart
  best   = TRUE,

  burnin = 1000,
  iter   = 6000,
  thin   = 100

We create a helping control that we can use when we need fast convergence for testing new code. Thus, the control parameters we use for fast testing are:
```{r fast control, eval = TRUE}
my_control_fast <- list(

@@

@@

###Extracting functions
The following functions are used as input in a map to compute and evaluate topic models. 
```{r extracting functions, eval = TRUE}
#extract dtm
extract_dtm <- function(origin) d_cast[[origin]]

@@

The following functions allow us to inspect the results from our models(inspect distributions and get kw):
```{r inspection functions, eval = TRUE}

@@

###Training Models
The function `train_topic_model` takes the type of text input ("catalogues", "manuals", c("catalogues", "manuals")) and number of topics to be trained. It fits an LDA model on the data and saves the output as a tibble where 
each row corresponds to a number of topics per text input (e.g. catalogues_50). It saves the DTM used to build the model, the corpus of origin (overview or manuals), the word and topic distributions results from that model, it's evaluation measures, and vectors of words and topics that allow us humans to get a feel of the model, along with some key words that will be used for the app.

```{r function train_model, eval = TRUE}
train_topic_model <- function(which_text, topic_numbers){
  topic_model <- tibble( 
    n_topic = rep(topic_numbers, each = length(d_text)) 
    ) %>%

    mutate(Origin     = rep(c("catalogues", "manuals"), length(topic_numbers)), 
           `Topic ID` = paste(Origin, n_topic, sep = "_"),

           #Document Term Matrix
           DTM        = pmap(.l = list(Origin), .f = extract_dtm)) %>%

  filter(Origin %in% which_texts) %>% ######################## was previously == instead of %in%

  mutate(
         #Fit Model
         Model  = pmap(.l = list(n_topic, DTM), .f = my_LDA, control = my_control_fast), #my_control

         #Select keywords
         kw = map(Beta, .f = get_kw)
         )
}

We apply the function separately and take the time it takes to fit the model.

Note: The manuals take a long time to run, we keep the trainings of catalogues and manuals separate so that changes in one do not require retraining the other. 
####Catalogues
```{r LDA fit catalogues, cache = TRUE, eval = TRUE}
#
## Catalogues

#Input vectors
which_texts <- "catalogues"
topic_numbers <-seq(from = 5, to = 150, by = 5)

#Intitial time
initial_time <- Sys.time()

#Application to catalogues
catalogues_topic_model <- train_topic_model(which_texts, topic_numbers)

#Final Time
final_time <- Sys.time()
took_how_long <- final_time - initial_time
print(paste(which_texts, took_how_long, sep =" "))

#Save
save(catalogues_topic_model, file = paste("./Output/", which_texts, "_topic_model_tibble.RDATA", sep = ""))
```

####Manuals
```{r LDA fit manuals, cache = TRUE, evel = TRUE }
#
## Manuals

#Input vectors
which_texts <- "manuals"

#Intitial time
initial_time <- Sys.time()

#Application to catalogues
manuals_topic_model <- train_topic_model(which_texts, topic_numbers)  #number of topics stayed the same cause we want to merge them.

#Final Time
final_time <- Sys.time()
took_how_long <- final_time - initial_time
print(paste(which_texts, took_how_long, sep =" "))

#Save
save(manuals_topic_model, file = paste("./Output/", which_texts, "_topic_model_tibble.RDATA", sep = ""))
```

```{r clean workspace functions, eval = TRUE}
# Clean workspace
# rm(extract_dtm, get_distributions, my_perplexity,
#    get_top_terms_topic, get_top_topics_course, get_kw)
```

If we trained separately but with the same number of topics, and wish to merge and save them:
```{r merge if trained separately, eval = TRUE}
cata <- catalogues_topic_model$n_topic
man  <- manuals_topic_model$n_topic

tb_topic_model <- tibble()

if(all(cata == man)){
  tb_topic_model <- rbind(catalogues_topic_model, manuals_topic_model)
}

save(tb_topic_model, file = "./Output/full_topic_model_tibble.RDATA")
```

##Plots - Model Evaluation
To evaluate how many topics are optiomal, we graph the perplexity and log Likelihood of models against the number of topics.
```{r perplexity plots, eval = TRUE}
#Function
plot_evaluation <- function(origin, data = tb_topic_model){

  #data
  data %>%

##Best model
We extract the best model for the catalogues and use it to innitialise the the second run of LDA algorithm with more burns and iterations
```{r best model, eval = T}
catalogues_tm <- tb_topic_model %>% fil
catalogue_dtm <- tb_topic_model$DTM[[1]]
catalogue_lda <- tb_topic_model %>% filter(n_topic == "65") %>% pull(Model) %>%.[[1]]

best_lda <- LDA(x = catalogue_dtm, 
                model = catalogue_lda, 
                control =  list(
                  nstart = 50,
                  seed   = 1 : 50, #must have length nstart
                  best   = TRUE,
                  burnin = 100,
                  iter   = 10000,
                  thin   = 2000) 
                )

save(best_lda, file = "./Output/catalogues_best_model.RDATA") 
```
##Best model pass to app
```{r}
load("./Output/catalogues_tmp_topic_model_tibble.RDATA")
load("./Output/catalogues_best_model.RDATA")

best_model <- tibble( 
  n_topic = 65
  ) %>%

  mutate(Origin     = "catalogues",
         `Topic ID` = paste(Origin, n_topic, sep = "_"),

@@

         #Fit Model
         Model  = list(best_lda),

@@

@@
